---
title: "Gallup - Assorted Regression Results"
author: "Daniel O'Leary"
date: "3/30/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer,
  broom,
  broom.mixed,
  gbm
)
```

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

dfg_rs <-
  read_rds("D:/data/gallup/exports/dfg_rs.rds")

dfg_rs <-
  dfg_rs %>% 
  mutate_at(
    vars(
      sex, 
      employment_all,
      race,
      married
    ),
    as.factor
  )
```

```{r}
contrasts(dfg_rs$sex) <- contr.sum(2)
contrasts(dfg_rs$employment_all) <- contr.sum(2)
contrasts(dfg_rs$race) <- contr.sum(5)
contrasts(dfg_rs$married) <- contr.sum(6)
```


## Demographic Median Income

### Height

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      height_scale,
      median_income_demo_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lmer(
      height_scale ~
        raw_income_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      height_scale ~
        raw_income_scale +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      height_scale ~
        median_income_demo_scale * raw_income_scale +
        median_income_demo_scale * education_scale +
        median_income_demo_scale * employment_all +
        median_income_demo_scale * sex +
        median_income_demo_scale * age_scale +
        median_income_demo_scale * race +
        median_income_demo_scale * married +
        median_income_demo_scale * year +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### Self-reported health

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      sr_health_scale,
      median_income_demo_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lmer(
      sr_health_scale ~
        raw_income_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      sr_health_scale ~
        raw_income_scale +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      sr_health_scale ~
        median_income_demo_scale * raw_income_scale +
        median_income_demo_scale * education_scale +
        median_income_demo_scale * employment_all +
        median_income_demo_scale * sex +
        median_income_demo_scale * age_scale +
        median_income_demo_scale * race +
        median_income_demo_scale * married +
        median_income_demo_scale * year +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### Life satisfaction

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      ladder_now_scale,
      median_income_demo_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lm(
      EHI_scale ~
        raw_income_scale +
        total_pop_county_scale +
        income_demo_ranger_sar_vars_scale +
        median_income_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year,
      #   (1 + raw_income_scale|fips_code),
      # REML = FALSE,
      # control = lmerControl(optimizer = "bobyqa"),
      data = dfg_rs
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      ladder_now_scale ~
        raw_income_scale +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      ladder_now_scale ~
        median_income_demo_scale * raw_income_scale +
        median_income_demo_scale * education_scale +
        median_income_demo_scale * employment_all +
        median_income_demo_scale * sex +
        median_income_demo_scale * age_scale +
        median_income_demo_scale * race +
        median_income_demo_scale * married +
        median_income_demo_scale * year +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### BMI

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      bmi_scale,
      median_income_demo_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lm(
      bmi_scale ~
        scale(income) +
        income_demo_ranger_sar_vars_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year,
      #   (1 + income_scale|fips_code),
      # REML = FALSE,
      # control = lmerControl(optimizer = "bobyqa"),
      #family = "binomial",
      data = dfg_rs
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      bmi_scale ~
        raw_income_scale +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      bmi_scale ~
        median_income_demo_scale * raw_income_scale +
        median_income_demo_scale * education_scale +
        median_income_demo_scale * employment_all +
        median_income_demo_scale * sex +
        median_income_demo_scale * age_scale +
        median_income_demo_scale * race +
        median_income_demo_scale * married +
        median_income_demo_scale * year +
        median_income_demo_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


## Geographic Median Income

### Height

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      height_scale,
      median_income_county_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lmer(
      height_scale ~
        raw_income_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      height_scale ~
        raw_income_scale +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      height_scale ~
        median_income_county_scale * raw_income_scale +
        median_income_county_scale * education_scale +
        median_income_county_scale * employment_all +
        median_income_county_scale * sex +
        median_income_county_scale * age_scale +
        median_income_county_scale * race +
        median_income_county_scale * married +
        median_income_county_scale * year +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### Self-reported health

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      sr_health_scale,
      median_income_county_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lmer(
      sr_health_scale ~
        raw_income_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      sr_health_scale ~
        raw_income_scale +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      sr_health_scale ~
        median_income_county_scale * raw_income_scale +
        median_income_county_scale * education_scale +
        median_income_county_scale * employment_all +
        median_income_county_scale * sex +
        median_income_county_scale * age_scale +
        median_income_county_scale * race +
        median_income_county_scale * married +
        median_income_county_scale * year +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### Life satisfaction

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      ladder_now_scale,
      median_income_county_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm1 <-
    lm(
      ladder_now_scale ~
        raw_income_scale +
        total_pop_county_scale +
        income_demo_ranger_scale +
        median_home_value_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year,
      data = data
    )

summary(lm1)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      ladder_now_scale ~
        raw_income_scale +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      ladder_now_scale ~
        median_income_county_scale * raw_income_scale +
        median_income_county_scale * education_scale +
        median_income_county_scale * employment_all +
        median_income_county_scale * sex +
        median_income_county_scale * age_scale +
        median_income_county_scale * race +
        median_income_county_scale * married +
        median_income_county_scale * year +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```


### BMI

#### Data selection

```{r}
dfg_current <-
  dfg_rs %>%
  filter_at(
    vars(
      bmi_scale,
      median_income_county_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  )
```


#### Baseline Model

```{r}
  lm0 <-
    lmer(
      bmi_scale ~
        raw_income_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm0)
  
tidy(lm0)

glance(lm0)
```


#### Main effect model

```{r}
  lm1 <-
    lmer(
      bmi_scale ~
        raw_income_scale +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        education_scale +
        employment_all +
        sex +
        age_scale +
        race +
        married + 
        year +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm1)
  
tidy(lm1)

glance(lm1)
```


#### Interactive model

```{r}
  lm2 <-
    lmer(
      bmi_scale ~
        median_income_county_scale * raw_income_scale +
        median_income_county_scale * education_scale +
        median_income_county_scale * employment_all +
        median_income_county_scale * sex +
        median_income_county_scale * age_scale +
        median_income_county_scale * race +
        median_income_county_scale * married +
        median_income_county_scale * year +
        median_income_county_scale +
        total_pop_county_scale +
        median_monthly_housing_cost_county_scale +
        land_area_2010_scale +
        physicians_scale +
        (1 + raw_income_scale|fips_code) +
        (1 + median_income_county_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
      data = dfg_current
    )

summary(lm2)
  
tidy(lm2)

glance(lm2)
```


#### Model comparison

```{r}
anova(lm0, lm1 , lm2)
```
