---
title: "Gallup Relative Status Health Behavior Regression Analysis"
author: "Daniel O'Leary"
date: "1/11/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer
)
```

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

source(paste0(machine_path, "research/projects/gallup/gallup_analysis_1/relative_status_analysis/regression_results_munge.R"))

dfg_rs <-
  read_rds("D:/data/gallup/exports/dfg_rs.rds")

dfg_rs <-
  read_rds("/Users/djolear/Google Drive/research/projects/gallup/gallup_data/relative_status/dfg_rs.rds")

dfg_rs <-
  dfg_rs %>% 
  mutate_at(
    vars(
      sex, 
      employment_all,
      race,
      married
    ),
    as.factor
  )
```

```{r}
contrasts(dfg_rs$sex) <- contr.sum(2)
contrasts(dfg_rs$employment_all) <- contr.sum(2)
contrasts(dfg_rs$race) <- contr.sum(5)
contrasts(dfg_rs$married) <- contr.sum(6)
```

```{r}
# c <- contr.treatment(2)
# c
# my.coding <- matrix(rep(1/2, 2), ncol = 1)
# my.simple = c - my.coding
# my.simple
# 
# contrasts(dfg_rs$sex) <- my.simple
# contrasts(dfg_rs$employment_all) <- my.simple
# 
# 
# c <- contr.treatment(5)
# my.coding <- matrix(rep(1/5, 20), ncol = 4)
# my.simple = c - my.coding
# my.simple
# 
# contrasts(dfg_rs$race) <- my.simple
# 
# 
# c <- contr.treatment(6)
# my.coding <- matrix(rep(1/6, 30), ncol = 5)
# my.simple = c - my.coding
# my.simple
# 
# contrasts(dfg_rs$married) <- my.simple
```


# Analysis

## Days w/ 5 servings of fruits and veggies

### Effect of median income

```{r}
fv_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("geo", "demo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  lmer(
    fruits_veggies_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + raw_income_scale|fips_code) +
      (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
    data = dfg_rs 
  )

summary(lm1)
```

### Interactive model

```{r}
lm2 <-
  lmer(
    fruits_veggies_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year +
      (1 + raw_income_scale|fips_code) +
      (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Eat healthy all day yesterday

### Effect of median income

```{r}
eh_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  glm(
    I(ifelse(fruits_veggies > 6, 1, ifelse(fruits_veggies %in% c(0:6), 0, NA))) ~
      raw_income_scale +
      median_income_demo_scale +
      #physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs 
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  glm(
    eat_healthy ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married,
    family = "binomial",
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Smoker?

### Effect of median income

```{r}
smoke_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  glm(
    smoke ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs  
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  glm(
    smoke ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married,
    family = "binomial",
    data = dfg_rs
  )

summary(lm2)
```

### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Purpose

### Effect of median income

```{r}
pur_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  lm(
    PURPOSE_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  lm(
    PURPOSE_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Financial

### Effect of median income

```{r}
fin_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  lm(
    FINANCIAL_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  lm(
    FINANCIAL_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Community

### Effect of median income

```{r}
com_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  lm(
    COMMUNITY_scale ~
      raw_income_scale +
      median_income_demo_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  lm(
    COMMUNITY_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Social

### Effect of median income

```{r}
soc_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("demo", "geo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("no id controls", "id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm1 <-
  lm(
    SOCIAL_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  lm(
    SOCIAL_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
# anova(lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm1, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Health outcomes

### BMI

```{r}
lm1 <-
  lm(
    bmi_scale ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)

lm1 <-
  lm(
    bmi_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```


### Diabetes

```{r}
lm1 <-
  glm(
    diabetes ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(diabetes = ifelse(diabetes == 1, 1, ifelse(diabetes == 2, 0, NA)))
  )

summary(lm1)

lm1 <-
  glm(
    diabetes ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(diabetes = ifelse(diabetes == 1, 1, ifelse(diabetes == 2, 0, NA)))
  )

summary(lm1)
```


### High blood pressure

```{r}
lm1 <-
  glm(
    hbp ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(hbp = ifelse(hbp == 1, 1, ifelse(hbp == 2, 0, NA)))
  )

summary(lm1)

lm1 <-
  glm(
    hbp ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(hbp = ifelse(hbp == 1, 1, ifelse(hbp == 2, 0, NA)))
  )

summary(lm1)
```


### Obesity

```{r}
lm1 <-
  glm(
    obese ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(obese = ifelse(obese == 1, 0, ifelse(obese == 0, 1, NA)))
  )

summary(lm1)

lm1 <-
  glm(
    obese ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    family = "binomial",
    data = dfg_rs %>% mutate(obese = ifelse(obese == 1, 0, ifelse(obese == 0, 1, NA)))
  )

summary(lm1)
```


### Self-reported health

```{r}
lm1 <-
  lm(
    scale(sr_health) ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs %>% mutate(sr_health = ifelse(sr_health %in% c(1:5), 6 - sr_health, NA))
  )

summary(lm1)

lm1 <-
  lm(
    scale(sr_health) ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs %>% mutate(sr_health = ifelse(sr_health %in% c(1:5), 6 - sr_health, NA))
  )

summary(lm1)
```


### Height

```{r}
lm1 <-
  lm(
    scale(HEIGHT) ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)

lm1 <-
  lm(
    scale(HEIGHT) ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    data = dfg_rs 
  )

summary(lm1)
```