---
title: "Gallup Relative Status Health Behavior Regression Analysis"
author: "Daniel O'Leary"
date: "1/11/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer
)
```

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

source(paste0(machine_path, "research/projects/gallup_rs/analysis/median_income_regressions/health_behavior_regression_munge.R"))

dfg_rs <-
  read_rds("D:/data/gallup/exports/dfg_rs.rds")

dfg_rs <-
  dfg_rs %>% 
  mutate_at(
    vars(
      sex, 
      employment_all,
      race,
      married
    ),
    as.factor
  )
```

```{r}
contrasts(dfg_rs$sex) <- contr.sum(2)
contrasts(dfg_rs$employment_all) <- contr.sum(2)
contrasts(dfg_rs$race) <- contr.sum(5)
contrasts(dfg_rs$married) <- contr.sum(6)
```
# Analysis

## Days w/ 5 servings of fruits and veggies

### Effect of median income

```{r}
fv_yearly <-
  fv_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("geographic reference", "demographic reference"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("", "id controls int."))) %>% 
  filter(id_controls != "no id controls" & id_controls != "id controls int.") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme_bw() +
  theme(
    text = element_text(size = 17),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  labs(
    y = "standardized beta for median income"
  ) +
  facet_grid(. ~ median_income_var) 


fv_yearly

ggsave(
  "G:/My Drive/research/projects/gallup_rs/plots/fv_yearly.png",
  fv_yearly,
  width = 8,
  height = 6,
  dpi = 500
)
```


### Main effects model

```{r}
lm0 <-
  lmer(
    fruits_veggies_scale ~
      raw_income_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + raw_income_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
    data = dfg_rs %>% filter(!is.na(median_income_demo_scale))
  )

summary(lm0)


lm1 <-
  lmer(
    fruits_veggies_scale ~
      raw_income_scale +
      median_income_county_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + raw_income_scale|fips_code) +
      (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
    data = dfg_rs 
  )

summary(lm1)
```

### Interactive model

```{r}
lm2 <-
  lmer(
    fruits_veggies_scale ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year +
      (1 + raw_income_scale|fips_code) +
      (1 + median_income_demo_scale|fips_code),
      REML = FALSE,
      control = lmerControl(optimizer = "bobyqa"),
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison

```{r}
# anova(lm0, lm1, lm2)
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Eat healthy all day yesterday

### Effect of median income

```{r}
eh_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("geo", "demo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```

```{r}
eh_yearly <-
  eh_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("geographic reference", "demographic reference"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("", "id controls int."))) %>% 
  filter(id_controls != "no id controls" & id_controls != "id controls int.") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme_bw() +
  theme(
    text = element_text(size = 17),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  labs(
    y = "standardized beta for median income"
  ) +
  facet_grid(. ~ median_income_var) 

eh_yearly

ggsave(
  "G:/My Drive/research/projects/gallup_rs/plots/eh_yearly.png",
  eh_yearly,
  width = 8,
  height = 6,
  dpi = 500
)
```


### Main effects model

```{r}
lm0 <-
  glm(
    eat_healthy ~
      raw_income_scale +
      #median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs  %>% filter(!is.na(median_income_demo_scale))
  )

lm1 <-
  glm(
    eat_healthy ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs  %>% filter(!is.na(median_income_demo_scale))
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  glm(
    eat_healthy ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married,
    family = "binomial",
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
anova(lm0, lm1, lm2,  test = "Chisq")
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```


## Smoker?

### Effect of median income

```{r}
smoke_terms %>% 
  filter(term == "median_income_var_scale") %>% 
  mutate(median_income_var = factor(median_income_var, labels = c("geo", "demo"))) %>% 
  mutate(id_controls = factor(id_controls, labels = c("id controls m.e.", "id controls int."))) %>% 
  filter(id_controls != "no id controls") %>% 
  mutate(year = as.factor(year)) %>% 
  ggplot(aes(year, estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.1) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    y = "median income"
  ) +
  facet_grid(id_controls ~ median_income_var)
```


### Main effects model

```{r}
lm0 <-
  glm(
    smoke ~
      raw_income_scale +
      #median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs  %>% filter(!is.na(median_income_demo_scale))
  )


lm1 <-
  glm(
    smoke ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married +
      year,
    family = "binomial",
    data = dfg_rs  
  )

summary(lm1)
```


### Interactive model

```{r}
lm2 <-
  glm(
    smoke ~
      median_income_demo_scale * raw_income_scale +
      median_income_demo_scale * education_scale +
      median_income_demo_scale * employment_all +
      median_income_demo_scale * sex +
      median_income_demo_scale * age_scale +
      median_income_demo_scale * race +
      median_income_demo_scale * married +
      median_income_demo_scale * year +
      physicians_scale +
      unweighted_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married,
    family = "binomial",
    data = dfg_rs
  )

summary(lm2)
```


### Model comparison 

```{r}
anova(lm0, lm1, lm2, test = "Chisq")
```


### Interaction plots

```{r}
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "education_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "raw_income_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "age_scale"))
plot_model(lm2, type = "pred", terms = c("median_income_demo_scale", "sex"))
```

