---
title: "Gallup - Comparing Demographic Reference Median Incomes"
author: "Daniel O'Leary"
date: "5/28/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer,
  broom,
  regclass
)
```

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

dfg_rs <-
  read_rds("D:/data/gallup/exports/dfg_rs.rds")

dfg_rs <-
  dfg_rs %>% 
  mutate_at(
    vars(
      sex, 
      employment_all,
      race,
      married
    ),
    as.factor
  )
```

```{r, include = FALSE}
linear_models_outcomes_wc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/linear_models_outcomes_wc.csv") %>% 
  mutate(
    cov = "yes"
  )

linear_models_outcomes_woc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/linear_models_outcomes_woc.csv") %>% 
  mutate(
    cov = "no"
  )

linear_models_outcomes <-
  linear_models_outcomes_wc %>% 
  left_join(
    linear_models_outcomes_woc,
    by = c("mi_var", "outcome_key")
  ) %>% 
  mutate(
    mi_value_diff = `scale(mi_value).x` - `scale(mi_value).y`
  )
```

```{r, include = FALSE}
linear_models_mediators_wc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/linear_models_mediators_wc.csv") %>% 
  mutate(
    cov = "yes"
  )

linear_models_mediators_woc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/linear_models_mediators_woc.csv") %>% 
  mutate(
    cov = "no"
  )

linear_models_mediators <-
  linear_models_mediators_wc %>% 
  left_join(
    linear_models_mediators_woc,
    by = c("mi_var", "outcome_key")
  ) %>% 
  mutate(
    mi_value_diff = `scale(mi_value).x` - `scale(mi_value).y`
  )
```


```{r, include = FALSE}
logistic_models_outcomes_wc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/logistic_models_outcomes_wc.csv") %>% 
  mutate(
    cov = "yes"
  )

logistic_models_outcomes_woc <- 
  read_csv("D:/data/gallup/results/many_models_reference_income/logistic_models_outcomes_woc.csv") %>% 
  mutate(
    cov = "no"
  )

logistic_models_outcomes <-
  logistic_models_outcomes_wc %>% 
  left_join(
    logistic_models_outcomes_woc,
    by = c("mi_var", "outcome_key")
  ) %>% 
  mutate(
    mi_value_diff = `scale(mi_value).x` - `scale(mi_value).y`
  )
```

```{r}
source("G:/My Drive/research/projects/gallup_rs/analysis/median_income_regressions/comparing demographic reference incomes/comparing_demographic_reference_incomes_plot_functions.R")
```


# Analysis

## Correlations among reference incomes

```{r}
dfg_rs %>% 
  dplyr::select(
    age_scale,
    education_scale,
    sex,
    starts_with("median_income_demo")
  ) %>% 
  mutate_all(as.numeric) %>% 
  dplyr::select(age_scale, education_scale, sex, median_income_demo_sa_scale:median_income_demo_esaiq_scale) %>% 
  cor(., use = "pairwise.complete.obs") %>% 
  round(., 2)
```

## Linear models for focal outcomes

### Coefficients with covariates

```{r}
coef_plot("scale(mi_value)", linear_models_outcomes_wc)
```


### Coefficients w/o covariates

```{r}
coef_plot("scale(mi_value)", linear_models_outcomes_woc)
```


### Difference in coefficients

```{r}
coef_diff_plot("mi_value_diff", linear_models_outcomes)
```


## Logistic models for focal outcomes

### Coefficients with covariates

```{r}
coef_plot("scale(mi_value)", logistic_models_outcomes_wc)
```


### Coefficients w/o covariates

```{r}
coef_plot("scale(mi_value)", logistic_models_outcomes_woc)
```


### Difference in coefficients

```{r}
coef_diff_plot("mi_value_diff", logistic_models_outcomes)
```


## Linear models for mediators

### Coefficients with covariates

```{r}
coef_plot("scale(mi_value)", linear_models_mediators_wc)
```


### Coefficients w/o covariates

```{r}
coef_plot("scale(mi_value)", linear_models_mediators_woc)
```


### Difference in coefficients

```{r}
coef_diff_plot("mi_value_diff", linear_models_mediators)
```


## Median differences in coefficients

### Linear models for focal outcomes

```{r}
linear_models_outcomes %>% 
  group_by(mi_var) %>% 
  summarise(
    median_coef_diff = median(mi_value_diff)
  )
```


### Logistic models for focal outcomes

```{r}
logistic_models_outcomes %>% 
  group_by(mi_var) %>% 
  summarise(
    median_coef_diff = round(median(mi_value_diff), 2)
  )
```

### Linear models for mediators

```{r}
linear_models_mediators %>% 
  group_by(mi_var) %>% 
  summarise(
    median_coef_diff = round(median(mi_value_diff), 2)
  )
```


## And this

```{r}
lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esa_scale,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      education_scale,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)
```


## What happens when we don't control for only demographics that are used in the reference income

### Fruits \ veggies

```{r}
lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      education_scale +
      employment_all +
      race +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)


lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_sar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      education_scale +
      employment_all +
      education_scale +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    fruits_veggies_scale ~
      scale(income) +
      median_income_demo_esar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)
```


### Cantril ladder

```{r}
lm1 <-
  lm(
    ladder_now_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      race +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)


lm1 <-
  lm(
    ladder_now_scale ~
      scale(income) +
      median_income_demo_sar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      education_scale +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    ladder_now_scale ~
      scale(income) +
      median_income_demo_esar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)
```


### Sense of purpose

```{r}
lm1 <-
  lm(
    PURPOSE_scale ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      race +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)


lm1 <-
  lm(
    PURPOSE_scale ~
      scale(income) +
      median_income_demo_sar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      education_scale +
      employment_all +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)

lm1 <-
  lm(
    PURPOSE_scale ~
      scale(income) +
      median_income_demo_esar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      married + 
      year,
    dfg_rs
  )

summary(lm1)
VIF(lm1)
```


### Smoking

```{r}
lm1 <-
  glm(
    smoke ~
      scale(income) +
      median_income_demo_esa_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      race +
      married + 
      year,
    dfg_rs,
    family = "binomial"
  )

summary(lm1)
VIF(lm1)


lm1 <-
  glm(
    smoke ~
      scale(income) +
      median_income_demo_sar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      education_scale +
      employment_all +
      education_scale +
      married + 
      year,
    dfg_rs,
    family = "binomial"
  )

summary(lm1)
VIF(lm1)

lm1 <-
  glm(
    smoke ~
      scale(income) +
      median_income_demo_esar_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      physicians_scale +
      employment_all +
      education_scale +
      married + 
      year,
    dfg_rs,
    family = "binomial"
  )

summary(lm1)
VIF(lm1)
```






