---
title: "Gallup - Relative Income - Mediation Analysis"
author: "Daniel O'Leary"
date: "5/20/2021"
output:
  github_document:
    toc: true
    toc_depth: 5
---

# Setup

## Load pacakges

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse, 
  haven,
  lme4,
  lm.beta,
  sjPlot,
  stargazer,
  broom,
  broom.mixed
)
```


## Load data

```{r, include = FALSE}
sinfo <- data.frame(Sys.info())
machine <- sinfo$Sys.info..[4]

machine_path <- 
  ifelse(
    machine %in% c("sussman-rp-mbpro.local", "sussman-rp-mbpro.lan"), 
    "/Users/djolear/Google Drive/", 
    "G:/My Drive/"
  )

dfg_rs <-
  read_rds("D:/data/gallup/exports/dfg_rs.rds")

dfg_rs <-
  dfg_rs %>% 
  mutate_at(
    vars(
      sex, 
      employment_all,
      race,
      married
    ),
    as.factor
  )
```


## Select relevant data

```{r}
data <-
  dfg_rs %>%
  filter_at(
    vars(
      eat_healthy,
      fruits_veggies_scale,
      smoke,
      median_income_demo_scale,
      education_scale,
      raw_income_scale,
      median_home_value_county_scale,
      median_monthly_housing_cost_county_scale,
      physicians_scale,
      PURPOSE_scale,
      COMMUNITY_scale,
      FINANCIAL_scale,
      SOCIAL_scale,
      PHYSICAL_scale,
      # neg_aff_scale,
      enough_money_scale,
      comp_satis_std_liv_scale,
      # bmi_scale,
      total_pop_county_scale,
      land_area_2010_scale,
      race,
      sex,
      age_scale,
      married,
      employment_all,
      year
    ),
    all_vars(!is.na(.))
  ) %>%
  dplyr::select(
    eat_healthy,
    fruits_veggies_scale,
    smoke,
    median_income_demo_scale,
    education_scale,
    raw_income_scale,
    median_home_value_county_scale,
    median_monthly_housing_cost_county_scale,
    physicians_scale,
    PURPOSE_scale,
    COMMUNITY_scale,
    FINANCIAL_scale,
    SOCIAL_scale,
    PHYSICAL_scale,
    # neg_aff_scale,
    enough_money_scale,
    comp_satis_std_liv_scale,
    # bmi_scale,
    total_pop_county_scale,
    land_area_2010_scale,
    age_scale,
    race,
    sex,
    married,
    employment_all,
    year,
    fips_code
  ) %>%
  #dummy_cols(., select_columns = c("sex", "race", "married", "employment_all")) %>%
  mutate(across(eat_healthy:land_area_2010_scale, as.numeric)) %>%
  mutate(across(sex:year, as.factor)) 
```


## Functions

```{r}
extract_med_coef <- function(lm) {
  
  # save lm object to variable
  coefs <- summary(lm)
  
  # extract coefficients
  coefs <- coefs$coefficients
  
  # select coefficient for relative income
  ri_coef <- coefs[3, 1]
  
  # return value
  return(ri_coef)
}

extract_outcome_coefs_med1 <- function(lm) {
    
  # save lm object to variable
  coefs <- summary(lm)
  
  # extract coefficients
  coefs <- coefs$coefficients
  
  # select coefficients for mediators
  coefs <- data.frame(t(coefs[2:6, 1]))
  
  # return values
  return(coefs)
}

extract_outcome_coefs_med2 <- function(lm) {
    
  # save lm object to variable
  coefs <- summary(lm)
  
  # extract coefficients
  coefs <- coefs$coefficients
  
  # select coefficients for mediators
  coefs <- data.frame(t(coefs[2:7, 1]))
  
  # return values
  return(coefs)
}

calculate_indirect_effects_med2 <- function(lm, coef_pur, coef_em, coef_cs, coef_com, coef_soc) {
  coefs_out <- extract_outcome_coefs_med2(lm)

  ie_pur <- coefs_out$PURPOSE_scale * coef_pur
  ie_em <- coefs_out$enough_money_scale * coef_em
  ie_cs <- coefs_out$comp_satis_std_liv_scale * coef_cs
  ie_com <- coefs_out$COMMUNITY_scale * coef_com
  ie_soc <- coefs_out$social_subset_scale * coef_soc

  total_effect = ie_pur + ie_em + ie_cs + ie_com + ie_soc + coefs_out$median_income_demo_scale

  res <-
    data.frame(
      "mediatior" = c("purpose", "enough_money", "comp_satis_living", "community", "social_subset"),
      "indirect_effects" = c(ie_pur, ie_em, ie_cs, ie_com, ie_soc)
    )

  res <-
    res %>% 
    mutate(
      prop_mediated = indirect_effects / total_effect
    )
  
  return(res)
}
```



# Analysis

## Mediation Analysis 1: Well-Being Composites

### Mediator models

```{r}
lm_pur <-
  lmer(
    PURPOSE_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_fin <-
  lmer(
    FINANCIAL_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_com <-
  lmer(
    COMMUNITY_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_soc <-
  lmer(
    SOCIAL_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


### Outcome models

#### Fruit and vegetable consumption

```{r}
lm_fv <-
  lmer(
    fruits_veggies_scale ~
      PURPOSE_scale +
      FINANCIAL_scale + 
      COMMUNITY_scale +
      SOCIAL_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


#### Eat healthy all day yesterday

```{r}
lm_eh <-
  lmer(
    eat_healthy ~
      PURPOSE_scale +
      FINANCIAL_scale + 
      COMMUNITY_scale +
      SOCIAL_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


#### Smoking

```{r}
lm_sm <-
  lmer(
    smoke ~
      PURPOSE_scale +
      FINANCIAL_scale + 
      COMMUNITY_scale +
      SOCIAL_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


### Indirect effects

```{r}
coef_pur <- extract_med_coef(lm_pur)
coef_fin <- extract_med_coef(lm_fin)
coef_com <- extract_med_coef(lm_com)
coef_soc <- extract_med_coef(lm_soc)
```


#### Fruit and vegetable consumption

```{r}
fv_ie <- calculate_indirect_effects_med1(lm_fv, coef_pur, coef_fin, coef_com, coef_soc)
fv_ie
```


#### Eat healthy all day yesterday

```{r}
eh_ie <- calculate_indirect_effects_med1(lm_eh, coef_pur, coef_fin, coef_com, coef_soc)
eh_ie
```


#### Smoking

```{r}
sm_ie <- calculate_indirect_effects_med1(lm_sm, coef_pur, coef_fin, coef_com, coef_soc)
sm_ie
```


## Mediation Analysis 2: Well-Being Composites with Financial and Social Subsets

### Mediator models

```{r}
lm_pur <-
  lmer(
    PURPOSE_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_em <-
  lmer(
    enough_money_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_cs <-
  lmer(
    comp_satis_std_liv_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_com <-
  lmer(
    COMMUNITY_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )

lm_soc <-
  lmer(
    social_subset_scale ~
      raw_income_scale +
      median_income_demo_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


### Outcome models

#### Fruit and vegetable consumption

```{r}
lm_fv <-
  lmer(
    fruits_veggies_scale ~
      PURPOSE_scale +
      enough_money_scale + 
      comp_satis_std_liv_scale
      COMMUNITY_scale +
      social_subset_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


#### Eat healthy all day yesterday

```{r}
lm_eh <-
  lmer(
    eat_healthy ~
      PURPOSE_scale +
      enough_money_scale + 
      comp_satis_std_liv_scale
      COMMUNITY_scale +
      social_subset_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


#### Smoking

```{r}
lm_sm <-
  lmer(
    smoke ~
      PURPOSE_scale +
      enough_money_scale + 
      comp_satis_std_liv_scale
      COMMUNITY_scale +
      social_subset_scale +
      median_income_demo_scale +
      raw_income_scale +
      physicians_scale +
      total_pop_county_scale +
      median_monthly_housing_cost_county_scale +
      land_area_2010_scale +
      education_scale +
      employment_all +
      sex +
      age_scale +
      race +
      married + 
      year +
      (1 + median_income_demo_scale | fips_code) +
      (1 + raw_income_scale | fips_code),
    REML = FALSE,
    control = lmerControl(optimizer = "bobyqa"),
    data = data 
  )
```


### Indirect effects

```{r}
coef_pur <- extract_med_coef(lm_pur)
coef_em <- extract_med_coef(lm_em)
coef_cs <- extract_med_coef(lm_cs)
coef_com <- extract_med_coef(lm_com)
coef_soc <- extract_med_coef(lm_soc)
```


#### Fruit and vegetable consumption

```{r}
fv_ie <- calculate_indirect_effects_med2(lm_fv, coef_pur, coef_em, coef_cs, coef_com, coef_soc)
fv_ie
```


#### Eat healthy all day yesterday

```{r}
eh_ie <- calculate_indirect_effects_med2(lm_eh, coef_pur, coef_em, coef_cs, coef_com, coef_soc)
eh_ie
```


#### Smoking

```{r}
sm_ie <- calculate_indirect_effects_med2(lm_sm, coef_pur, coef_em, coef_cs, coef_com, coef_soc)
sm_ie
```
